---
title: "SVM and Bagging & RF"
description: |
  Support Vector Machine and Bagging and Random Forest Exercise 
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    code_folding: true
---

# Exercise 1 (Bootstrap)
## 1. Redo the bootstrap analysis, but use 10 samples. Change times = 100 to times = 10. How does the population estimate for mean change?
###     - The population estimate does not change after changing the number of samples. 
```{r}
library(curl)
load(curl("https://raw.githubusercontent.com/Professor-Hunt/ACC8143/main/data/tips.rda"))

set.seed(0)
library(rsample)
library(tidyverse)

#perform bootstrapping with 2000 replications
resample2 <- bootstraps(as.data.frame(tips$size), times = 10)

#mean
mean(resample2$splits[[1]]$data$`tips$size`)
#standard deviation
sd(resample2$splits[[1]]$data$`tips$size`)
```

## 2. Redo the bootstrap analysis, but find the median. What is the difference in population estimate for the median vs mean?
###     - Population estimate for median and mean is different. Median is 2 while mean is 2.569672. 
```{r}
resample1 <- bootstraps(as.data.frame(tips$size), times = 100)
median(resample1$splits[[1]]$data$`tips$size`)
mean(resample1$splits[[1]]$data$`tips$size`)
```
# Exercise 1 (SVM)
## 1. Change the training to testing split size, for example change from a 60%:40% to a 75%:25%, and to a 50%:50%. Compare the results to the 60/40.
###     - Compared to the resuls to the 60:40, accuracy and kappa were bigger when testing size was 75:25 and 50:50. Also, they were biggest when the size of testing sample was 50%. 
```{r}
library(caret)
library(tidyverse)
#set the seed :)
set.seed(1)
trainIndex <- createDataPartition(iris$Species, p = .75, list = FALSE, times = 1)

#grab the data
SVMTrain <- iris[ trainIndex,]
SVMTest  <- iris[-trainIndex,]

iris_SVM <- train(
  form = factor(Species) ~ .,
  data = SVMTrain,
  #here we add classProbs because we want probs
  trControl = trainControl(method = "cv", number = 10,
                           classProbs =  TRUE),
  method = "svmLinear",
  preProcess = c("center", "scale"),
  tuneLength = 10)

iris_SVM
```

```{r}

trainIndex50 <- createDataPartition(iris$Species, p = .5, list = FALSE, times = 1)

#look at the first few
#head(trainIndex)

#grab the data
SVMTrain50 <- iris[ trainIndex50,]
SVMTest50  <- iris[-trainIndex50,]


iris_SVM50 <- train(
  form = factor(Species) ~ .,
  data = SVMTrain50,
  #here we add classProbs because we want probs
  trControl = trainControl(method = "cv", number = 10,
                           classProbs =  TRUE),
  method = "svmLinear",
  preProcess = c("center", "scale"),
  tuneLength = 10)

iris_SVM50
```

## 2. Change the Kernel…use svmPoly for the method. method = "svmLinear", to method = "svmPoly", compare the linear results with the polynomial results.
```{r}
set.seed(1)
#get our samples
#using the iris data
#lets split the data 60/40

trainIndex22 <- createDataPartition(iris$Species, p = .6, list = FALSE, times = 1)

#look at the first few
#head(trainIndex)

#grab the datas
SVMTrain22 <- iris[ trainIndex22,]
SVMTest22  <- iris[-trainIndex22,]


iris_SVM22 <- train(
  form = factor(Species) ~ .,
  data = SVMTrain22,
  #here we add classProbs because we want probs
  trControl = trainControl(method = "cv", number = 10,
                           classProbs =  TRUE),
  method = "svmPoly",
  preProcess = c("center", "scale"),
  tuneLength = 10)

iris_SVM22
```





